Bootstrap Confidence Intervals for Sharp Regression Discontinuity Designs with the Uniform Kernel

### 2016-02-29 main_paper.tex
Remove trailing whitespace from main LaTeX file

The intuition behind both procedures is very straightforward. CCT show that a
local second order polynomial captures all of the unmodeled aspects of the DGP
necessary for constructing valid confidence intervals. Our proposed algorithms
estimate and embed the second order behavior in the bootstrap DGP through
a residual bootstap.
Algorithm~\ref{Alg1} explains the bias-correction steps in detail.

@@

The Monte Calro experiments have a similar structure. For all of them, we
generate 500 i.i.d.\ observations from the DGP
\begin{align*}
Y_{i}           &= \mu_{j}(X_{i}) + \varepsilon_{i} \\
X_{i}           &\sim  2 \times \betarv(2,4) - 1 \\
\varepsilon_{i} &\sim \normal(0, 0.1295^2),
\end{align*}
where $j$ will index the specific DGP. This is the experimental design used by
\citet{IK} CCT, which we adopt here to make our simulation results directly
comparable with theirs and more comparable with the rest of the literature. We
will use the same three functional forms for $\mu_j$ as CCT as well.

\nocite{lee2008rand}%
The first DGP is designed to match features of Lee's (2008) analysis of U.S.\
congressional elections. Lee estimates the incumbency advantage in electoral
races for the House of Representatives --- candidates who received the largest
vote share in the previous election are the incumbants, which creates the
discontinuity. The conditional expectation is a fifth order polynomial fit to
that dataset, (after excluding a small number of extreme observations; see
\citealp{IK}, or CCT for further details) giving
\begin{equation*}
  \mu_{1}(x) =
  \begin{cases}
    0.48 + 1.27x + 7.18x^{2} + 20.21x^{3} + 21.54x^{4} + 7.33x^{5}
    & \textif\ x < 0 \\
    0.52 + 0.84x - 3.00x^{2} + 7.99x^3 - 9.01x^4 + 3.56x^{5}
    & \otherwise.
  \end{cases}
\end{equation*}
The population ATE for this DGP is $0.04$ $(= 0.52 - 0.48)$.

\nocite{ludwig2007}%
The second DGP is based on Ludwig and Miller's (2007) analysis of the Head Start
program. Funding eligability is determined at the county level using the
county's historical poverty rate, with a sharp threshold that determines the
provision of services. We use the fifth order polynomial estimated on Ludwig and
Miller's dataset as the conditional expectation for the second DGP:
\begin{equation*}
  \mu_{2}(x) =
  \begin{cases}
    3.71 + 2.30x + 3.28x^2 + 1.45x^3 + 0.23x^4 + 0.03x^5
    & \textif\ x < 0, \\
    0.26 + 18.49x - 54.81x^2 + 74.30x^3 - 45.02x^4 + 9.83x^5
    & \otherwise
  \end{cases}
\end{equation*}
and the population ATE is $-3.45$ $(= 0.26 - 3.71)$.

@@

To estimate the finite-sample coverage of our new bootstrap interval, we
simulate 1500 samples from each of the three DGPs and calculate nominal 95\%
two-sided confidence intervals. We use 999 bootstrap replications ($B_2$) to
cacluate the asymptotic distribution of the bias corrected estimator, and each
of those replications uses an additional 500 replications ($B_1$) to estimate
the bias. We use the $0.025$ and $0.975$ quantiles of the bootstrap distribution
as the lower and upper bound of the interval, and the bandwidths, $h$ and $b$,
are chosen using the AMSE-optimal rule proposed by CCT.

@@

It is important not to read too much into these simulation results. Where there
are differences between these procedures, they are small enough that randomness
in the simulations is likely a factor in their precise rankings.\footnote{%
  To help address this concern, we are currently running a more extensive set of
  simulations and will update this paper when they are complete.} %
These are DGPs where the naive confidence intervals are known to perform poorly,
and this set of simulation results indicates that our proposed bootstrap approach
is quite competetive with analytical methods for producing valid intervals.
Overall, the bootstrap bias-correction procedure proposed in this paper provides
a simple alternative to obtain valid robust confidence intervals in RD designs
and performs well compared to the analytical bias correction procedures proposed
by CCT.

>>>>

The intuition behind both procedures is very straightforward. CCT show that a
local second order polynomial captures all of the unmodeled aspects of the DGP
necessary for constructing valid confidence intervals. Our proposed algorithms
estimate and embed the second order behavior in the bootstrap DGP through
a residual bootstrap.
Algorithm~\ref{Alg1} explains the bias-correction steps in detail.

@@

The Monte Carlo experiments have a similar structure. For all of them, we
generate 500 i.i.d.\ observations from the DGP
\begin{align*}
Y_{i}           &= \mu_{j}(X_{i}) + \varepsilon_{i} \\
X_{i}           &\sim  2 \times \betarv(2,4) - 1 \\
\varepsilon_{i} &\sim \normal(0, 0.1295^2),
\end{align*}
where $j$ will index the specific DGP. This is the experimental design used by
\citet{IK} CCT, which we adopt here to make our simulation results directly
comparable with theirs and more comparable with the rest of the literature. We
will use the same three functional forms for $\mu_j$ as CCT as well.

\nocite{lee2008rand}%
The first DGP is designed to match features of Lee's (2008) analysis of U.S.\
congressional elections. Lee estimates the incumbency advantage in electoral
races for the House of Representatives --- candidates who received the largest
vote share in the previous election are the incumbents, which creates the
discontinuity. The conditional expectation is a fifth order polynomial fit to
that dataset, (after excluding a small number of extreme observations; see
\citealp{IK}, or CCT for further details) giving
\begin{equation*}
  \mu_{1}(x) =
  \begin{cases}
    0.48 + 1.27x + 7.18x^{2} + 20.21x^{3} + 21.54x^{4} + 7.33x^{5}
    & \textif\ x < 0 \\
    0.52 + 0.84x - 3.00x^{2} + 7.99x^3 - 9.01x^4 + 3.56x^{5}
    & \otherwise.
  \end{cases}
\end{equation*}
The population ATE for this DGP is $0.04$ $(= 0.52 - 0.48)$.

\nocite{ludwig2007}%
The second DGP is based on Ludwig and Miller's (2007) analysis of the Head Start
program. Funding eligibility is determined at the county level using the
county's historical poverty rate, with a sharp threshold that determines the
provision of services. We use the fifth order polynomial estimated on Ludwig and
Miller's dataset as the conditional expectation for the second DGP:
\begin{equation*}
  \mu_{2}(x) =
  \begin{cases}
    3.71 + 2.30x + 3.28x^2 + 1.45x^3 + 0.23x^4 + 0.03x^5
    & \textif\ x < 0, \\
    0.26 + 18.49x - 54.81x^2 + 74.30x^3 - 45.02x^4 + 9.83x^5
    & \otherwise
  \end{cases}
\end{equation*}
and the population ATE is $-3.45$ $(= 0.26 - 3.71)$.

@@

To estimate the finite-sample coverage of our new bootstrap interval, we
simulate 1500 samples from each of the three DGPs and calculate nominal 95\%
two-sided confidence intervals. We use 999 bootstrap replications ($B_2$) to
calculate the asymptotic distribution of the bias corrected estimator, and each
of those replications uses an additional 500 replications ($B_1$) to estimate
the bias. We use the $0.025$ and $0.975$ quantiles of the bootstrap distribution
as the lower and upper bound of the interval, and the bandwidths, $h$ and $b$,
are chosen using the AMSE-optimal rule proposed by CCT.

@@

It is important not to read too much into these simulation results. Where there
are differences between these procedures, they are small enough that randomness
in the simulations is likely a factor in their precise rankings.\footnote{%
  To help address this concern, we are currently running a more extensive set of
  simulations and will update this paper when they are complete.} %
These are DGPs where the naive confidence intervals are known to perform poorly,
and this set of simulation results indicates that our proposed bootstrap approach
is quite competitive with analytical methods for producing valid intervals.
Overall, the bootstrap bias-correction procedure proposed in this paper provides
a simple alternative to obtain valid robust confidence intervals in RD designs
and performs well compared to the analytical bias correction procedures proposed
by CCT.
